---
title: "Hypothesis_Testing"
author: "Nicolas Bievre, Harry Emeric"
date: "03/12/2019"
output:
  html_document:
    df_print: paged
---

This Rmd file contains cells which clean the Kickstarter data, prepare it for causal analysis on the three 
treatments we are considering: 'is_project_we_love', 'is_first_project_from_creator', 'has_one_dollar_reward'. We 
then carry out hypothesis tests based on Neyman's and Fisher's frameworks.

```{r, include=FALSE, comment=NA, echo=FALSE}
library(knitr)
library(kableExtra)
library(magrittr)
library(ggplot2)
library(faraway)
library(DOS2)
library(RItools)
library(optmatch)
library(sensitivitymult)
library(dplyr)

# Contains methods used in analysis
source('utility.R')

set.seed(0) 
```


# MAIN R PIPELINE

# Load data

```{r, include=TRUE, comment=NA, echo=TRUE}
# SAMPLE FIRST 1000
kickstarter_data <- read.csv('../data/kickstarter_data.csv')
```


# Define columns to work with

## List of all columns

```{r, include=TRUE, comment=NA, echo=TRUE}
x <- c( 'avg_reward_description',
        'blurb_length',
        'blurb_word_count',
        'category_art',
        'category_comics',
        'category_crafts',
        'category_dance',
        'category_design',
        'category_fashion',
        'category_film_video',
        'category_food',
        'category_games',
        'category_journalism',
        'category_music',
        'category_photography',
        'category_publishing',
        'category_technology',
        'category_theater',
        'country_at',
        'country_au',
        'country_be',
        'country_ca',
        'country_ch',
        'country_de',
        'country_dk',
        'country_es',
        'country_fr',
        'country_gb',
        'country_hk',
        'country_ie',
        'country_it',
        'country_jp',
        'country_lu',
        'country_mx',
        'country_nl',
        'country_no',
        'country_nz',
        'country_se',
        'country_sg',
        'country_us',
        'creator_project_no',
        'duration_campaign_creation_to_launch',
        'duration_campaign_launch_to_deadline',
        'faq',
        'has_faq',
        'has_one_dollar_reward',
        'is_asking_for_help',
        'is_not_first_project_from_creator',
        'is_project_we_love',
        'name_length',
        'name_word_count',
        'rewards_levels',
        'rewards_max',
        'rewards_mean',
        'rewards_min',
        'state',
        'usd_goal',
        'usd_pledged'
        )
```

# Define Treatment

## List of possible treatments

```{r, include=TRUE, comment=NA, echo=TRUE}
# treatment <- 'is_asking_for_help'
# treatment <- 'is_not_first_project_from_creator'
# treatment <- 'is_project_we_love'
# treatment <- 'has_faq'
# treatment <- 'has_one_dollar_reward'

kickstarter_data <- kickstarter_data %>%
  mutate(control=as.numeric(is_not_first_project_from_creator+is_project_we_love+has_one_dollar_reward==0),
         T1=as.numeric((is_not_first_project_from_creator==1)&(is_project_we_love+has_one_dollar_reward==0)),
         T2=as.numeric((is_project_we_love==1)&(is_not_first_project_from_creator+has_one_dollar_reward==0)),
         T3=as.numeric((has_one_dollar_reward==1)&(is_not_first_project_from_creator+is_project_we_love==0)))


kickstarter_data %>% group_by(control,T1,T2,T3) %>% summarise(n())

```

# Define outcome

# Pre preprocess data

## Keep only columns of interest

```{r, include=TRUE, comment=NA, echo=TRUE}
#kickstarter_data <- kickstarter_data[, (names(kickstarter_data) %in% x)]
```

## Add treatment to the data under column z

```{r, include=TRUE, comment=NA, echo=TRUE}
#names(kickstarter_data)[names(kickstarter_data) == treatment] <- 'z'
```

## Add outcome to the data under column y

```{r, include=TRUE, comment=NA, echo=TRUE}
outcome <- 'state'
names(kickstarter_data)[names(kickstarter_data) == outcome] <- 'y'
```




# Remove outliers

## With outliers

```{r, include=TRUE, comment=NA, echo=TRUE}
ggplot(kickstarter_data, aes(y = usd_pledged)) + 
  geom_boxplot(fill = "#4271AE", colour =  "#1F3552", alpha = 0.7) +
  ggtitle("Boxplot of usd_pledged with outliers")
```

## Without outliers

### Remove outliers

```{r, include=TRUE, comment=NA, echo=TRUE}
outliers <- boxplot(kickstarter_data$usd_pledged, plot=FALSE)$out
kickstarter_data <- kickstarter_data[-which(kickstarter_data$usd_pledged %in% outliers),]

#outliers <- boxplot(kickstarter_data$usd_goal, plot=FALSE)$out
#kickstarter_data <- kickstarter_data[-which(kickstarter_data$usd_goal %in% outliers),]
```

```{r, include=TRUE, comment=NA, echo=TRUE}
ggplot(kickstarter_data, aes(y = usd_pledged)) + 
  geom_boxplot(fill = "#4271AE", colour =  "#1F3552", alpha = 0.7) +
  ggtitle("Boxplot of usd_pledged without outliers") 
```

## Filtering

```{r}
# Less than $1k goal 
kickstarter_data <- kickstarter_data %>% filter(usd_goal>1000)
nrow(kickstarter_data)
```

# Exploratory analysis

```{r, include=TRUE, comment=NA, echo=TRUE}
head(kickstarter_data)
```


```{r, include=TRUE, comment=NA, echo=TRUE}
#summary(kickstarter_data)
```

## Define Treatment

```{r}
# T1
kickstarter_data$z <- kickstarter_data$T1
kickstarter_data <- kickstarter_data %>% filter(z+control==1) %>% select(-c(control,T1,T2,T3))
```

# Vizualisations 

## USD pledged density visualization

```{r, include=TRUE, comment=NA, echo=TRUE}
ggplot(data=kickstarter_data, aes(x=usd_pledged, group=as.factor(z), fill=as.factor(z))) +
  geom_density(alpha=0.5) + 
  theme_bw() +
  scale_fill_discrete(name = "", labels = c('Control', 'Treatment')) +
  theme(legend.position = "top")
```


## Box vizualisation


```{r, include=TRUE, comment=NA, echo=TRUE}
ggplot(kickstarter_data, aes(x = category_art, y = usd_pledged, group=as.factor(z))) + 
  geom_boxplot(aes(fill = as.factor(z)))
```


# Methods

## Data structure to save the results

```{r, include=TRUE, comment=NA, echo=TRUE}
hypothesis.results <- data.frame('when' = c(), 
                                 'tau' = c(),
                                 'V' = c(),
                                 'CI_lower' = c(),
                                 'CI_upper' = c(),
                                 'p_Fisher' = c(),
                                 'p_Neyman' = c(),
                                 'Gamma' = c())
```

## Estimator

```{r, include=TRUE, comment=NA, echo=TRUE}
N0 <- sum(1 - kickstarter_data$z)
N1 <- sum(kickstarter_data$z)
N <- N0 + N1
```


```{r, include=TRUE, comment=NA, echo=TRUE}
tau_obs <- sum(kickstarter_data$z*kickstarter_data$y) / N1 - sum((1-kickstarter_data$z)*kickstarter_data$y) / N0
formatC(tau_obs, format = "e", digits = 4)
```


```{r, include=TRUE, comment=NA, echo=TRUE}
Y0_mean <- ((1-kickstarter_data$z)*kickstarter_data$y)/N0
Y1_mean <- (kickstarter_data$z*kickstarter_data$y)/N1

V0 <- sum(((1-kickstarter_data$z)*kickstarter_data$y - Y0_mean)^2)/(N0-1)
V1 <- sum((kickstarter_data$z*kickstarter_data$y - Y1_mean)^2)/(N1-1)

V10 <- sum((kickstarter_data$z*kickstarter_data$y - (1-kickstarter_data$z)*kickstarter_data$y) - (Y1_mean -Y0_mean))/(N-1)

V <- V1/N1 + V0/N0
formatC(V, format = "e", digits = 4)
```


# Neyman's CI

```{r, include=TRUE, comment=NA, echo=TRUE}
# Upper bound
CI.upper <- tau_obs + 1.96*sqrt(V/N)
formatC(CI.upper, format = "e", digits = 4)

# Lower bound
CI.lower <- tau_obs - 1.96*sqrt(V/N)
formatC(CI.lower, format = "e", digits = 4)
```

# Neyman's p-value

```{r}
p_Neyman <- pnorm((tau_obs-0)/sqrt(V),lower.tail = FALSE)
p_Neyman
```

# Fisher permutation test

```{r, include=TRUE, comment=NA, echo=TRUE}
Fisher_test.max_iter <- 1000
Power.max_iter <- 1000
alpha = 0.05
```

## Perform Fisher permutation test

```{r, include=TRUE, comment=NA, echo=TRUE}
T = c()
for(i in 1:Fisher_test.max_iter) {
  z <- sample(kickstarter_data$z, N, replace=FALSE)
  T[i] = sum(z*kickstarter_data$y)/N1 - sum((1 - z)*kickstarter_data$y)/N0
}
```

## P value

```{r, include=TRUE, comment=NA, echo=TRUE}
p.Fisher = mean(as.numeric(T >= tau_obs))
formatC(p.Fisher, format = "e", digits = 5)
```

## Power of the test

```{r, include=TRUE, comment=NA, echo=TRUE, eval = FALSE}
P = c()
for(j in 1:Power.max_iter) {
  T = c()
  for(i in 1:Fisher_test.max_iter) {
    z <- sample(kickstarter_data$z, N, replace=FALSE)
    T[i] = sum(z*kickstarter_data$y)/N1 - sum((1 - z)*kickstarter_data$y)/N0
  }
  P[j] = mean(as.numeric(T >= tau_obs))
}
```


```{r, include=TRUE, comment=NA, echo=TRUE, eval = FALSE}
power.Fisher <- mean(as.numeric(P <= alpha))
formatC(power.Fisher, format = "e", digits = 4)
```



# Matching

```{r}
# Covariates
x <- c( 'blurb_word_count',
        'category_art',
        'category_comics',
        'category_crafts',
        'category_dance',
        'category_design',
        'category_fashion',
        'category_film_video',
        'category_food',
        'category_games',
        'category_journalism',
        'category_music',
        'category_photography',
        'category_publishing',
        'category_technology',
        'category_theater',
        'country_at',
        'duration_campaign_launch_to_deadline',
        'has_faq',
        'is_asking_for_help',
        'rewards_levels',
        'rewards_max',
        'rewards_mean',
        'rewards_min',
        'usd_goal'
        )

x <- c( 'blurb_word_count',
        'category_art',
        'category_comics',
        'category_crafts',
        'category_dance',
        'category_design',
        'category_fashion',
        'category_film_video',
        'category_food',
        'category_games',
        'category_journalism',
        'category_music',
        'category_photography',
        'category_publishing',
        'category_technology',
        'category_theater',
        'country_at',
        'duration_campaign_launch_to_deadline',
        'has_faq',
        'is_asking_for_help',
        'rewards_levels',
        'rewards_max',
        'rewards_mean',
        'rewards_min'
        )


```



```{r}
library(pastecs)
attach(kickstarter_data[,x])
scores <- c(blurb_word_count,
        category_art,
        category_comics,
        category_crafts,
        category_dance,
        category_design,
        category_fashion,
        category_film_video,
        category_food,
        category_games,
        category_journalism,
        category_music,
        category_photography,
        category_publishing,
        category_technology,
        category_theater,
        country_at,
        duration_campaign_launch_to_deadline,
        has_faq,
        is_asking_for_help,
        rewards_levels,
        rewards_max,
        rewards_mean,
        rewards_min
        )
options(scipen=100)
options(digits=0)
tbl <- stat.desc(scores,basic=TRUE)
toKeep <- c("nbr.val","min","max","mean","median","std.dev")
#tbl <- t(tbl[toKeep,])
detach(kickstarter_data[,x])
write.csv(tbl,'../results/covariateDescStats.csv')

#summary(kickstarter_data[,x])

```

## Balance of daa

```{r, include=TRUE, comment=NA, echo=TRUE}
plot(xBalance(z ~ creator_project_no + duration_campaign_launch_to_deadline +
                faq + has_faq + has_one_dollar_reward + is_asking_for_help + 
                is_project_we_love + name_length + name_word_count + rewards_levels,
              data=kickstarter_data))
```





```{r, include=TRUE, comment=NA, echo=TRUE}
#plot(xBalance(z ~ . - y,data=kickstarter_data))
```





## Propensity scores

```{r, include=TRUE, comment=NA, echo=TRUE}
#kickstarter_data$prop <- glm(z ~ avg_reward_description + blurb_length + blurb_word_count + category_art + category_comics + category_crafts + category_dance + category_design + category_fashion + category_film_video + category_food + category_games + category_journalism + category_music + category_photography + category_publishing + category_technology + category_theater + country_at + country_au + country_be + country_ca + country_ch + country_de + country_dk + country_es + country_fr + country_gb + country_hk + country_ie + country_it + country_jp + country_lu + country_mx + country_nl + country_no + country_nz + country_se + country_sg + country_us + has_one_dollar_reward + is_asking_for_help + duration_campaign_creation_to_launch + duration_campaign_launch_to_deadline + is_project_we_love + name_length + name_word_count  + rewards_levels + rewards_max + rewards_mean + rewards_min + faq + has_faq ,
#                             family=binomial,
#                             data=kickstarter_data)$fitted.values

#toRemove <- c("creator_project_no","usd_goal","usd_pledged",'is_not_first_project_from_creator','state')
#covariates <- x[!c(x %in% toRemove)]
categories <- colnames(kickstarter_data)[grepl("^category_",colnames(kickstarter_data))]
#covariates_to_match <- c("avg_reward_description","blurb_word_count","duration_campaign_launch_to_deadline",
#                         "has_faq","rewards_levels","rewards_mean","has_one_dollar_reward",categories)
  
fmla <- as.formula(paste('z~',paste0(x,collapse='+')))
plot(xBalance(fmla,data=kickstarter_data))
kickstarter_data$prop <- glm(fmla, family=binomial, data=kickstarter_data)$fitted.values

# Remove creator_project_no  + usd_goal + usd_pledged 
```

The density of the propensity scores is showed with the code bellow:

```{r, include=TRUE, comment=NA, echo=TRUE}
ggplot(data=kickstarter_data, aes(x=prop, group=as.factor(z), fill=as.factor(z))) + 
  geom_density(alpha=0.5) + theme_bw()
```

## Multivariate matching

```{r}
match.nocaliper <- smahal(kickstarter_data$z, kickstarter_data[,x])
ms.nocaliper <- pairmatch(match.nocaliper, data=kickstarter_data)
fmla <- as.formula(paste('z~',paste0(x,collapse='+'),'+ strata(ms.nocaliper) - 1'))
adat.1 <- summarize.match(kickstarter_data, ms.nocaliper)
plot(xBalance(fmla,data=kickstarter_data))

tau_obs_matched <- mean(adat.1$y.1 - adat.1$y.0)
tau_obs_matched

```


```{r}
mean_diff_before <- mean(abs(adat.1$prop.0 - adat.1$prop.1))
print(mean_diff_before)

max_diff_before <- max(abs(adat.1$prop.0 - adat.1$prop.1))
print(max_diff_before)

# Add propensity score caliper
match.withcaliper <- addcaliper(match.nocaliper, z=kickstarter_data$z, p=kickstarter_data$prop, caliper=0.1)
ms.withcaliper <- pairmatch(match.withcaliper, data=kickstarter_data)
adat.2 <- summarize.match(kickstarter_data, ms.withcaliper)
fmla <- as.formula(paste('z~',paste0(x,collapse='+'),'+ strata(ms.withcaliper) - 1'))
plot(xBalance(fmla,data=kickstarter_data))

tau_obs_matched <- mean(adat.2$y.1 - adat.2$y.0)

mean_diff_after <- mean(abs(adat.2$prop.0 - adat.2$prop.1))
print(mean_diff_after)

max_diff_after <- max(abs(adat.2$prop.0 - adat.2$prop.1))
print(max_diff_after)

```

## Sensitivity Analysis

```{r, include=TRUE, comment=NA, echo=TRUE}
data.senm <- cast.senm(kickstarter_data, ms.withcaliper, two.outcomes=FALSE)
s <- senm(data.senm$y, data.senm$z, mset=data.senm$mset, gamma = 1, inner = 0, trim = 'Inf')
s
```


```{r, include=TRUE, comment=NA, echo=TRUE}
data.senm <- cast.senm(kickstarter_data, ms.withcaliper, two.outcomes=FALSE)
Gamma <- NA
#senm(data.senm$y, data.senm$z, mset=data.senm$mset, gamma = Gamma, inner = 0, trim = 'Inf')
```


## Save results

```{r, include=TRUE, comment=NA, echo=TRUE}
hypothesis.results <- data.frame('when' = c(), 
                                 'tau' = c(),
                                 'V' = c(),
                                 'CI_lower' = c(),
                                 'CI_upper' = c(),
                                 'p_Fisher' = c(),
                                 'p_Neyman' = c(),
                                 'Gamma' = c())
  
  
current.results <- data.frame('when' = c('before matching'), 
                              'tau' = c(tau_obs),
                              'p_Fisher' = c(p.Fisher),
                              'p_Neyman' = c(p_Neyman),
                               'V' = c(V),
                               'CI_lower' = c(CI.lower),
                               'CI_upper' = c(CI.upper),
                               #'power_Fisher' = c(""),
                               'Gamma' = NA)

de <- data.frame('when' = c('after matching'), 
                              'tau' = c(tau_obs_matched),
                              'p_Fisher' = c(s$pval),
                              'p_Neyman' = c(''),
                               'V' = c(''),
                               'CI_lower' = c(''),
                               'CI_upper' = c(''),
                               #'power_Fisher' = c(""),
                               'Gamma' = c(Gamma))

newdf <- rbind(current.results, de)
newdf

# Set this to name of your experiment
csvname <- "H3_HasOneDollarReward"
f <- paste0('../results/',csvname,'.csv')

if (!file.exists(f)) {
  write.csv(newdf, f)
} else print("File exists already")

```



```{r, include=TRUE, comment=NA, echo=TRUE}
col <- 'usd_pledged' 
ggplot(data=kickstarter_data, aes(x=col, group=z)) +
  geom_density(alpha=0.5) +
  theme_bw() + 
  scale_fill_discrete(name = "Group", labels = c('Control', 'Treatment')) +
  geom_vline(aes(xintercept=mean(col)), color="blue", linetype="dashed", size=1)
```


```{r, include=TRUE, comment=NA, echo=TRUE}
boxplot(kickstarter_data$usd_pledged, main = "After removing the outliers")
```



```{r, include=TRUE, comment=NA, echo=TRUE}
boxplot(kickstarter_data$usd_pledged, main = "After removing the outliers")
```

